Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-01 Geometric types.tex
Added Loc_H(G)

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
%To simplify notation below, set $H=G\der$.
Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
it is also an $H$-torsor in the fpqc topology.  
Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$
It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. \todo{Haven't defined $\Loc$ and $\Loc_{G\der}$}
Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
%
Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.

>>>>

\begin{proposition} \label{prop:CSGabab}
Suppose $G$ is a smooth group scheme.  
Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
\end{proposition}
\begin{proof}
%To simplify notation below, set $H=G\der$.
Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, it is also an $H$-torsor in the fpqc topology.  
Let $\Loc(G\ab)$ be the category of local systems on $G\ab$.
Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$.
Thus, objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that 
\[
\begin{tikzcd}
s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G} 
\end{tikzcd}
\]
commutes, where $s: G \to G\der\times G$ is $s(g) = (1,g)$ and such that the following diagram commutes, where $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$.
\[
\begin{tikzcd}
& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{n_2\circ p = n\circ p_2}& \\
n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L}  & 
\end{tikzcd}
\]
It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
%
Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.
